---
title: "Placeholder Vignette"
output: rmarkdown::html_vignette
# output: 
#   rmarkdown::html_vignette:
#     toc: true
#   pdf_document:
#     highlight: null
#     number_sections: yes
vignette: >
  %\VignetteIndexEntry{Placeholder Vignette}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r echo = F}
knitr::opts_chunk$set(echo = TRUE)
```

Note: **This vignette is illustrated with fake data**. The dataset explored in this example should not be used to inform decision-making.

```{r results='hide', message=FALSE, warning=FALSE}
library(avert)
```

This is a placeholder vignette that demonstrates the three illustrative functions that are bundled with the initial development version of the avert library.

## Identify the publicly available project repositories 
The `get_project_repos` function retrieves the names of publicly available repos in in the [avertableburden GitHub organisation](https://github.com/avertableburden).

```{r}
get_project_repos()
```
## Retrieve publicly available model parameters
The `get_input_data` function retrieves a list object that stores (currently, placeholder) model parameter values from the [public Dataverse dataset](https://doi.org/10.7910/DVN/QTJJLZ). 

```{r}
parameters_ls <- get_input_data()
```

The `get_parameter_value` function retrieves the values of named parameters from the parameter values list.

```{r}
get_parameter_value("first", parameters_ls)
```
```{r}
get_parameter_value("second", parameters_ls)
```
